Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2023-06-30 analysis/paper/London_HauloutBeahvior.Rmd
re-run analysis; troubleshoot data anomalies
after some updates to telemetry database, a few minor coding improvements, etc. I re-ran the analysis and, initially, had some errors that caused me to realize observations were present outside of the deployment period. Those issues were fixed and, now, models fit without error
update suppl table of deployments

```{r seal-hours}
create_yday_groups <- function(analysis_data) {
  d <- analysis_data %>%
    tibble::as_tibble() %>%
    dplyr::mutate(yday = lubridate::yday(haulout_dt)) %>%
    dplyr::select(yday) %>%
    dplyr::distinct() %>%
    dplyr::arrange(yday)

  d <- split(d$yday, ceiling(seq_along(d$yday) / 8)) %>%
    dplyr::as_tibble() %>%
    tidyr::pivot_longer(
      cols = 1:18,
      names_to = "col_group",
      values_to = "yday",
      names_transform = list(col_group = as.integer),
      values_transform = list(yday = as.integer)
    ) %>%
    dplyr::arrange(yday) %>% 
    transform(row_group = letters[1:8]) %>% 
    dplyr::filter(col_group < 18)
  return(d)
}

yday_groups <- create_yday_groups(analysis_data)

@@

* **Josh M. London**: investigation, conceptualization, methodology,
formal analysis, validation, software, writing: original draft, writing:
review and editing, visualization, and data curation
* **Paul B. Conn**: conceptualization, methodology, formal analysis,
software, validation, writing: original draft, writing: review and
editing
* **Stacie K. Hardy**: investigation, data curation, methodology,
validation, writing: review and editing
* **Erin L. Richmond**: data curation, investigation, methodology,
validation, writing: review and editing
* **Jay M. Ver Hoef**: conceptualization, methodology, software, writing:
review and editing
* **Michael F. Cameron**: investigation, project administration, writing:
review and editing
* **Justin Crawford**: investigation, methodology, validation, data curation, 
writing: review and editing
* **Lori T. Quakenbush**: investigation, methodology, supervision, project
administration, writing: review and editing
* **Andrew L. Von Duyke**: investigation, methodology, validation, data curation,
writing: review and editing
* **Peter L. Boveng**: investigation, conceptualization, supervision,
project administration, writing: review and editing

@@

The following table provides additional details about the timing, location, and
agencies responsible for the bio-logger deployments used in this study.

@@

@@

deploy_tbl %>% 
  dplyr::select(species, agency, deploy_year, permit, location, speno, sex, age, publications) %>% 
  dplyr::group_by(species, agency, deploy_year, location, publications) %>% 
  dplyr::mutate(agency = 
                  case_when(
                    agency %in% c('ADFG') ~ "Alaska Dept. Fish & Game",
                    agency %in% c('NSB') ~ "North Slope Burough",
                    agency %in% c('PEP') ~ "NOAA Alaska Fisheries Sci. Ctr",
                    agency %in% c('NPWC') ~ "N. Pacific Wildlife Consortium"
                  )) %>% 
  dplyr::summarise(permits = toString(unique(permit)),
                   n_seals = n(),
                   sex = toString(unique(sex)),
                   age_class = tolower(toString(unique(age)))) %>% 
  dplyr::arrange(species, agency, deploy_year) %>% 
  gt(
    rowname_col = "species",
    groupname_col = "agency"
  ) %>% 
  cols_label(
    deploy_year = "Year Deployed",
    location = "Location",
    publications = "Publication(s)",
    permits = "Permits",
    n_seals = "No. Seals",
    sex = "Sex",
    age_class = "Age Class"
  ) %>% 
  tab_style(
    style = list(
      cell_text(style = "italic")
    ),
    locations = cells_body(
      columns = publications
    )
  ) %>% 
  cols_align(
    align = "center",
    columns = everything()
  ) %>% 
  cols_align(
    align = "right",
    columns = age_class
  ) %>% 
  tab_header(
    title = "Data Contributions From Collaborators and Additional Deployment Details"
  )

>>>>

```{r seal-hours}
# create_yday_groups <- function(analysis_data) {
#   d <- analysis_data %>%
#     tibble::as_tibble() %>%
#     dplyr::mutate(yday = lubridate::yday(haulout_dt)) %>%
#     dplyr::select(yday) %>%
#     dplyr::distinct() %>%
#     dplyr::arrange(yday)
#   
#   d <- split(d$yday, ceiling(seq_along(d$yday) / 8)) %>%
#     dplyr::as_tibble() %>%
#     tidyr::pivot_longer(
#       cols = 1:15,
#       names_to = "col_group",
#       values_to = "yday",
#       names_transform = list(col_group = as.integer),
#       values_transform = list(yday = as.integer)
#     ) %>%
#     dplyr::arrange(yday) %>% 
#     transform(row_group = letters[1:8])
#   return(d)
# }
# 
# yday_groups <- create_yday_groups(analysis_data)

@@

* **Josh M. London**: investigation, conceptualization, methodology,
formal analysis, validation, software, writing: original draft, writing:
review and editing, visualization, and data curation
* **Paul B. Conn**: conceptualization, methodology, formal analysis,
software, validation, writing: original draft, writing: review and
editing
* **Stacie K. Hardy**: investigation, data curation, methodology,
validation, writing: review and editing
* **Erin L. Richmond**: data curation, investigation, methodology,
validation, writing: review and editing
* **Jay M. Ver Hoef**: conceptualization, methodology, software, writing:
review and editing
* **Michael F. Cameron**: investigation, project administration, writing:
review and editing
* **Justin A. Crawford**: investigation, methodology, validation, data curation, 
writing: review and editing
* **Lori T. Quakenbush**: investigation, methodology, supervision, project
administration, writing: review and editing
* **Andrew L. Von Duyke**: investigation, methodology, validation, data curation,
writing: review and editing
* **Peter L. Boveng**: investigation, conceptualization, supervision,
project administration, writing: review and editing

@@

The following table provides additional details about the timing, location, and
institutions responsible for the bio-logger deployments used in this study.

@@

options(
  gargle_oauth_cache = here::here(".secrets"),
  gargle_oauth_email = TRUE
)

gs4_auth()

@@

deploy_tbl <- deploy_tbl %>% 
  dplyr::select(species, agency, deploy_year, permit, location, speno, sex, age, publications) %>% 
  dplyr::group_by(species, agency, deploy_year, location, publications) %>% 
  dplyr::mutate(agency = 
                  case_when(
                    agency %in% c('ADFG') ~ "ADFG",
                    agency %in% c('NSB') ~ "NSB",
                    agency %in% c('PEP') ~ "NMFS",
                    agency %in% c('NPWC') ~ "NPWC"
                  )) %>% 
  dplyr::summarise(permits = toString(unique(permit)),
                   n_seals = n(),
                   sex = toString(unique(sex)),
                   age_class = tolower(toString(unique(age)))) %>% 
  dplyr::arrange(species, agency, deploy_year) %>% 
  gt(
    groupname_col = "species"
  ) %>% 
  cols_label(
    agency = "Institution",
    deploy_year = "Year Deployed",
    location = "Location",
    publications = "Publication(s)",
    permits = "Permits",
    n_seals = "No. Seals",
    sex = "Sex",
    age_class = "Age Class"
  ) %>% 
  tab_style(
    style = list(
      cell_text(style = "italic")
    ),
    locations = cells_body(
      columns = publications
    )
  ) %>% 
  cols_align(
    align = "center",
    columns = everything()
  ) %>% 
  cols_align(
    align = "right",
    columns = age_class
  ) %>% 
  tab_header(
    title = "Data Contributions From Collaborators and Additional Deployment Details"
  ) %>%
  tab_footnote(footnote = "ADF&G = Alaska Department of Fish and Game",
               locations = cells_body(columns = agency, 
                                      rows = agency == "ADFG")) %>%
  tab_footnote(footnote = "NSB = North Slope Borough",
               locations = cells_body(columns = agency, 
                                      rows = agency == "NSB")) %>%
  tab_footnote(footnote = "NMFS = NOAA National Marine Fisheries Service",
               locations = cells_body(columns = agency, 
                                      rows = agency == "NMFS")) %>%
  tab_footnote(footnote = "NPWC = North Pacific Wildlife Consortium",
               locations = cells_body(columns = agency, 
                                      rows = agency == "NPWC"))
